ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-25 pyked.tex
Update schema and API description with new format

The second section of the file encodes the experimental data. The \ck{} file
describes these using a sequence of mappings, with the following information required
in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units
    \item \yabox|pressure| (required, string): The pressure of the experiment,
    with units
    \item \yabox|composition| (required, sequence): The composition of the
    mixture in the experiment, described via a sequence of mappings with the fields
    \begin{itemize}
        \item \yabox|species-name| (required, string): The name of the species
        \item \yabox|mole-fraction|, \yabox|mole-percent|, \yabox|mass-fraction|
        (required, float): The mole fraction or percent, or the mass fraction.
        Only one of the three is permitted in a given \yabox|composition|
        sequence.
        \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
        \yabox|elemental-composition| (required, string or sequence): The InChI
        or SMILES representing the molecule, or its atomic or elemental
        composition (\yabox|atomic-composition| and
        \yabox|elemental-composition| are synonyms) as a sequence
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), or \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

@@

The fields of the \ck{} file are stored as instance attributes of the
\pybox|ChemKED| class. The following attributes are available:
%
\begin{itemize}
    \item \pybox|chemked_version|, \pybox|file_version|, \pybox|file_author|,
    \pybox|experiment_type|: Stores the values from the \ck{} file
    \item \pybox|reference|: Instance of a \pybox|namedtuple| containing all
    the information from the literature reference associated with the data
    \item \pybox|apparatus|: Instance of a \pybox|namedtuple| containing all
    the information about the apparatus used to perform the experiment
    \item \pybox|datapoints|: A Python list of \pybox|DataPoint| instances
\end{itemize}

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole-percent|,
    \yabox|mole-fraction|, or \yabox|mass-fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole-percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole-percent'|,
    \pybox|'mole-fraction'|, or \pybox|'mass-fraction'|
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: If the \ck{} file encodes an RCM experiment,
    the length of the compression stroke may be included
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}

>>>>

The second section of the file encodes the experimental data. The \ck{} file
describes these using a sequence of mappings, with the following information required
in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
            \yabox|elemental-composition| (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic or elemental
            composition (\yabox|atomic-composition| and\\
            \yabox|elemental-composition| are synonyms) as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), or \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

@@

The fields of the \ck{} file are stored as instance attributes of the
\pybox|ChemKED| class. The following attributes are available:
%
\begin{itemize}
    \item \pybox|chemked_version|, \pybox|file_version|, \pybox|file_author|,
    \pybox|experiment_type|: Store the ``meta'' values from the \ck{} file
    \item \pybox|reference|: Instance of a \pybox|namedtuple| containing all
    the information from the literature reference associated with the data
    \item \pybox|apparatus|: Instance of a \pybox|namedtuple| containing all
    the information about the apparatus used to perform the experiment
    \item \pybox|datapoints|: A Python \pybox|list| of \pybox|DataPoint| instances
\end{itemize}

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole-percent|,
    \yabox|mole-fraction|, or \yabox|mass-fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole-percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole-percent'|,
    \pybox|'mole-fraction'|, or \pybox|'mass-fraction'|
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: If the \ck{} file encodes an RCM experiment,
    the length of the compression stroke may be included
    \item \pybox|compressed_temperature|: If the \ck{} file encodes an RCM experiment,
    the temperature at the end of compression may be included
    \item \pybox|compressed_pressure|: If the \ck{} file encodes an RCM experiment,
    the pressure at the end of compression may be included
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}
